Evaluation of performances

### 2019-07-10 analysis/eval-performance.Rmd
update reports
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE, verbose = TRUE)

source(here::here("code/99-packages.R"))
sourceDirectory("R")

# load drake objects
loadd(
  bm_aggregated
)
library("mlr")
library("magrittr")
```

```{r eval-performance-1 }
bm_aggregated %>%
  getBMRAggrPerformances(as.df = TRUE) %>%
  arrange(task.id, desc(rmse.test.mean))
```

### Boxplot comparison

```{r performance-boxplot, dev = c("png", "pdf")}
plt <- plotBMRBoxplots(bm_aggregated,
  measure = brier, pretty.names = FALSE,
  # order.lrn = c(
  #   "classif.gam.tuned", 
  #   "classif.kknn.tuned",
  #   "classif.ranger.tuned",
  #   "classif.svm.tuned", 
  #   "classif.gbm.tuned",
  #   "classif.xgboost.tuned"
  # )
) +
  aes(color = learner.id) +
  geom_boxplot(width = 0.6, outlier.size = 0.3, outlier.shape = 19) +
  scale_colour_nejm() +
  labs(y = "Brier score", x = "") +
  theme_pubr() +
  theme(strip.text.x = element_text(size = 8),
        axis.text.x = element_text(size = 7)
        )

#levels(plt$data$learner.id) <- c("GAM", "KNN", "RF", "SVM", "BRT", "XGBOOST")

plt
```

@@

```{r performance-aggregated, dev = c("png", "pdf")}
plt2 <- plotBMRSummary(bm_aggregated, pretty.names = FALSE) +
  scale_colour_nejm() +
  theme_pubr()

#levels(plt$data$learner.id) <- c("GAM", "KNN", "RF", "SVM", "BRT", "XGBOOST")

plt2
```

>>>>

R.utils::sourceDirectory("R")

# load drake objects
drake::loadd(
  bm_aggregated
)
library("mlr")
library("magrittr")
library("dplyr")
library("ggplot2")
library("ggrepel")
library("ggsci")
library("ggpubr")
```

@@

#### (Table) All leaner/filter/task combinations ordered by performance.

```{r eval-performance-1}
getBMRAggrPerformances(bm_aggregated, as.df = TRUE) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI"
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  ) %>%
  group_by(learner_group, task.id, filter) %>%
  summarise(best = min(rmse.test.rmse)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(best) %>%
  knitr::kable()
```

#### (Table) Best learner/filter/task combination

```{r eval-performance-2}
getBMRAggrPerformances(bm_aggregated, as.df = TRUE) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  ) %>%
  group_by(learner_group) %>%
  slice(which.min(rmse.test.rmse)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(rmse.test.rmse) %>%
  select(-6) %>%
  knitr::kable()
```

#### (Plot) Best learner/filter combs for all tasks

```{r eval-performance-3}
results_aggr <- getBMRAggrPerformances(bm_aggregated, as.df = TRUE) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI"
  )) %>%
  tidyr::separate(learner.id, c("learner_group"),
    remove = FALSE,
    sep = " "
  ) %>%
  group_by(learner_group, task.id) %>%
  summarise(best = min(rmse.test.rmse))

results_aggr %>%
  ggplot(aes(x = best, y = task.id)) +
  geom_point(aes(color = learner_group, size = 1.7)) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(1.8, 4)) +
  geom_label_repel(
    label = round(results_aggr$best, 3),
    size = 3, nudge_y = 0.3
  ) +
  theme_pubr()
```
